Supporting Information

### 2020-01-09 manuscript/manuscript.Rmd
Added results to main ms for labeling strategy; added figure for corresponding probability images to SI

These problems arising from cropland characteristics are increasingly being overcome due to technological advances. Recent advances in satellite technology have increased the coverage of high (<5 m) or near-high (10 m) resolution imagery with weekly to near-daily return intervals [@DruschSentinel2ESAOptical2012; @McCabefutureEarthobservation2017]. This spatial and temporal resolution addresses the sensor-scale mismatch, and more effectively captures the intra-seasonal dynamics of cropland, which helps classifiers distinguish cropland from surrounding cover types [@Debatsgeneralizedcomputervision2016; @Defournyrealtimeagriculturemonitoring2019]. On top of this, advances in cloud computing [@GorelickGoogleEarthEngine2017a], the opening of image archives [@WulderglobalLandsatarchive2016], and next generation machine learning approaches [@MaxwellImplementationmachinelearningclassification2018; @ZhuDeeplearningremote2017] are placing large volumes of these moderate to near-high resolution imagery together with the computational and algorithmic resources necessary to classify them at scale. These capabilities are aleady being used to create a new generation of higher resolution (20-30 m) cropland and landcover maps for Africa and other regions [@ChenGloballandcover2015; @ESAESACCILAND; @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017].

@@

### Classification pipeline
Upon completion of the labels, *labeller* automatically launches an ephemeral Elastic Map Reduce cluster consisting of tens to hundreds of instances (e.g. m4.xlarge), depending on the size of the mapping geography.

@@

To more fully evaluate the capacities of different components of the system, we performed several experiments. In the first experiments, we evaluated the degree to which training label quality impacts final map accuracy, by comparing maps created by training the RandomForest algorithm with labels created by the least accurate worker, the most accurate worker, in addition to those trained with the consensus labels. This test aligns with Tier 1 standards for accounting for the impact of training data error on final map accuracy, as recommended by @ElmesAccountingtrainingdata2019. Next, we evaluated the degree to which training sample selection via active learning impacted map accuracy relative to random selection of additional training sites. Related to this, we evaluated two different versions of the active learning uncertainty criterion to evaluate the impact on performance gain.

@@

# Results
```{r, echo=FALSE, message=FALSE, warning=FALSE}
tiles <- sf::read_sf(system.file("extdata/ghana_tiles.geojson", 
                                 package = "activemapper"))
km2 <- round(as.numeric(units::set_units(sum(sf::st_area(tiles)), "km2")))
```
We developed maps for all of Ghana (`r km2` km$^2$). Ghana's has several agro-ecologically distinct regions, ranging from the primarily grain and vegetable crop producing regions in the drier northern savanna regions to tree crop dominated regions in the forested southwestern corner of the country, where cocoa and oil palm are among the dominant crops. For these latter regions, we did not attempt to classify tree crops, and instead mapped clearings that potentially contain field crops or recently felled or newly replanted tree crops. Our rationale for this decision was that the resolution of PlanetScope imagery is insufficient to distinguish such crops from the surrounding forest, and clear field boundaries are typically not visible in cocoa crops.

@@

## System evaluation/experiment results
### Label quality and map accuracy
```{r, echo=FALSE}
load(here::here("external/data/label_experiment_metrics.rda"))
consensus <- scores %>% filter(Label == "Consensus") %>% 
  select(AUC, Accuracy, TSS) 
high <- scores %>% filter(Label == "High") %>% select(AUC, Accuracy, TSS) 
low <- scores %>% filter(Label == "Low") %>% select(AUC, Accuracy, TSS)
auc <- high$AUC / low$AUC - 1
tss <- (high$TSS + 1) / (low$TSS + 1) - 1
acc <- high$Accuracy / low$Accuracy - 1
cauc <- consensus$AUC / high$AUC - 1
ctss <- (consensus$TSS + 1) / (high$TSS + 1) - 1
cacc <- consensus$Accuracy / high$Accuracy - 1
```

@@

```{r, echo = FALSE, out.height = "4in", out.width="7in", fig.cap="Difference in overall, user's, and producer's accuracy between maps made with consensus labels, the least accurate worker's, and most accurate worker's labels. [This a hypothetical placeholder figure].", fig.align='center', message=FALSE}
knitr::include_graphics('figures/figure6.png')
# library(tidyverse)
# library(cowplot)
# set.seed(1)
# acc_tb <- tibble(aoi = c(1:9, 12, 15), 
#                  Consensus = runif(11, min = 0.75, max = 0.85),
#                  Highest = runif(11, min = 0.72, max = 0.8),
#                  Least = runif(11, min = 0.65, max = 0.75))
# acc_tb <- gather(acc_tb, key = "type", value = "score", -aoi)
# ggplot(acc_tb) + 
#   geom_boxplot(aes(x = type, y = score), fill = "grey") + 
#   xlab("Labelling strategy") + ylab("Accuracy") + 
#   theme(panel.grid.major.y = element_line(colour = "grey80", linetype = 3))
```

@@

###

>>>>

These problems arising from cropland characteristics are increasingly being overcome due to technological advances. Recent advances in satellite technology have increased the coverage of high (<5 m) or near-high (10 m) resolution imagery with weekly to near-daily return intervals [@DruschSentinel2ESAOptical2012; @McCabefutureEarthobservation2017]. This spatial and temporal resolution addresses the sensor-scale mismatch, and more effectively captures the intra-seasonal dynamics of cropland, which helps classifiers distinguish cropland from surrounding cover types [@Debatsgeneralizedcomputervision2016; @Defournyrealtimeagriculturemonitoring2019]. On top of this, advances in cloud computing [@GorelickGoogleEarthEngine2017], the opening of image archives [@WulderglobalLandsatarchive2016], and next generation machine learning approaches [@MaxwellImplementationmachinelearningclassification2018; @ZhuDeeplearningremote2017] are placing large volumes of these moderate to near-high resolution imagery together with the computational and algorithmic resources necessary to classify them at scale. These capabilities are aleady being used to create a new generation of higher resolution (20-30 m) cropland and landcover maps for Africa and other regions [@ChenGloballandcover2015; @ESAESACCILAND; @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017].

@@

### Classification pipeline
Upon completion of the labels, *labeller* automatically launches an ephemeral Elastic Map Reduce cluster consisting of tens to hundreds of instances, depending on the size of the mapping geography. We identifed an optimal cluster of 50-60 instances (m4.2xlarge) each having 8 virtual CPUs and 30 GB RAM, which ensured minimal idle time for any single node.

@@

To more fully evaluate the capacities of different components of the system, we performed several experiments. In the first experiments, we evaluated the degree to which training label quality impacts final map accuracy, by comparing maps created by training the RandomForest algorithm with labels created by the least accurate worker, the most accurate worker, in addition to those trained with the consensus labels. This test aligns with Tier 1 standards for accounting for the impact of training data error on final map accuracy, as recommended by @ElmesAccountingtrainingdata2019. Next, we evaluated the degree to which training sample selection via active learning impacted map accuracy relative to random selection of additional training sites.

<!-- Related to this, we evaluated two different versions of the active learning uncertainty criterion to evaluate the impact on performance gain.  -->

@@

# Results
```{r, echo=FALSE, message=FALSE, warning=FALSE}
tiles <- sf::read_sf(system.file("extdata/ghana_tiles.geojson", 
                                 package = "activemapper"))
km2 <- round(as.numeric(units::set_units(sum(sf::st_area(tiles)), "km2")))
km2 <- format(km2, big.mark = ",", scientific = FALSE)
```
We developed maps for all of Ghana (`r km2` km$^2$). Ghana has several agro-ecologically distinct regions, ranging from the primarily grain and vegetable crop producing regions in the northern savannas to tree crop-dominated system in the forested southwest, where cocoa and oil palm are among the dominant crops. For these latter regions, we did not attempt to classify tree crops, and instead mapped clearings that potentially contain field crops or recently felled or newly replanted tree crops. Our rationale for this decision was that the resolution of PlanetScope imagery is insufficient to distinguish such crops from the surrounding forest, and clear field boundaries are typically not visible in cocoa crops.

@@

## System evaluation
### Label quality and map accuracy
```{r, echo=FALSE}
load(here::here("external/data/label_experiment_metrics.rda"))
consensus <- scores %>% filter(Label == "Consensus") %>% 
  select(AUC, Accuracy, TSS) 
high <- scores %>% filter(Label == "High") %>% select(AUC, Accuracy, TSS) 
low <- scores %>% filter(Label == "Low") %>% select(AUC, Accuracy, TSS)
auc <- high$AUC / low$AUC - 1
tss <- (high$TSS + 1) / (low$TSS + 1) - 1
acc <- high$Accuracy / low$Accuracy - 1
cauc <- consensus$AUC / high$AUC - 1
ctss <- (consensus$TSS + 1) / (high$TSS + 1) - 1
cacc <- consensus$Accuracy / high$Accuracy - 1
```

@@

```{r, echo = FALSE, out.width="100%", fig.cap="Difference in overall, user's, and producer's accuracy between maps made with consensus labels, the least accurate worker's, and most accurate worker's labels.", fig.align='center', message=FALSE}
knitr::include_graphics('figures/figure6.png')
# library(tidyverse)
# library(cowplot)
# set.seed(1)
# acc_tb <- tibble(aoi = c(1:9, 12, 15), 
#                  Consensus = runif(11, min = 0.75, max = 0.85),
#                  Highest = runif(11, min = 0.72, max = 0.8),
#                  Least = runif(11, min = 0.65, max = 0.75))
# acc_tb <- gather(acc_tb, key = "type", value = "score", -aoi)
# ggplot(acc_tb) + 
#   geom_boxplot(aes(x = type, y = score), fill = "grey") + 
#   xlab("Labelling strategy") + ylab("Accuracy") + 
#   theme(panel.grid.major.y = element_line(colour = "grey80", linetype = 3))
```

@@

### Is active learning any better than random? 
To evaluate whether active learning is more effective than a purely random approach to training site selection, we retrained the RandomForest model on the same three AOIs (1, 8, 15) using sites that were selected purely at random for all iterations after the initial training draw. After the mapping team labelled these sites, we subsequently retrained the models with each increment of randomly selected sites, and evaluated prediction performance against the original validation set.

### 2020-01-09 manuscript/si.Rmd
Added results to main ms for labeling strategy; added figure for corresponding probability images to SI

>>>>

\clearpage
# Results

```{r, echo = FALSE, out.width="100%", fig.cap="Cropland probability images produced by RandomForest models trained with A) consensus labels, B) the most accurate worker's labels, and C) the least accurate worker's labels.", fig.align='center', message=FALSE}
knitr::include_graphics('figures/si_hml_probs.png')
```
